Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-02 paper/figures.Rnw
Tinkering with onset/offset facet wrap

    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=onOffLevels)) %>%
        cast(county + variable ~ pctile)

@@

<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = stateThresholdsByWindow %>% 
        melt(id=c("epiyear")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=onOffLevels)) %>%
        cast(epiyear + variable ~ pctile)

>>>>

    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        cast(county + variable ~ pctile) %>%
        mutate(variable=factor(variable, levels=onOffLevels))

@@

<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = stateThresholdsByWindow %>% 
        melt(id=c("epiyear")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        cast(epiyear + variable ~ pctile) %>%
        mutate(variable=factor(variable, levels=onOffLevels))
